---
title: 'Test-run #2: annual data'
author: "Jessica Couture"
date: "August 12, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F,message = F)
```

## Parameters added to SPASM package: "Attraction"

**farmStay**  
To account for changes in adult movement, I added a parameter, `farmStay` that is basically a divisor for the probability of adult movement inside the farm area.  
--> must use density_dependence_for = 2 for `farmStay` to work

**habFactor**
SPASM has the `mpa_habfactor` built in already, which adjusts the recruitment rates inside the MPA/farm area. Therefore I adjust this to increase juvenile abundance in the area. Does not account for movement of juveniles though, so could be insignificant if juv.movement is high.

In the test runs below I also vary farm `size`, which is a percent of the total area, and the `adult_movement` parameter whose effect depends on the relative size of the modeled space.

Other parameters used in this run:

* Numer of patches = 100
* Juv. movement = 5
* Adult movement = 7
* Fish sp. = _P. virens_
* Fishing = "constant effort" (@ effort = 2000); reaction to MPA = "concentrate"
* density_dependence_form = 2

```{r data}

library(tidyverse)
library(cowplot)

sfh<-read_csv("testRunSFHY.csv")

```

## Adult movement inhibitor: *Farm stay*

```{r just_farmStay, echo=FALSE}

fs20<-sfh%>%
  filter(size==0.2)%>%
  filter(habFact==1)

fs_s20<-ggplot(fs20,aes(year,ppue,color=as.factor(farmStay),group=as.factor(farmStay)))+
  geom_line()+
  theme_bw()+
  lims(y=c(10,16))+
  labs(y="Price / effort",title = "Farm size = 20%")+
  theme(legend.position = "none")


fs70<-sfh%>%
  filter(size==0.7)%>%
  filter(habFact==1)

fs_s70<-ggplot(fs70,aes(year,ppue,color=as.factor(farmStay),group=as.factor(farmStay)))+
  geom_line()+
  theme_bw()+
  lims(y=c(10,16))+
  labs(y="Price / effort",title = "Farm size = 70%")+
  scale_color_discrete(name="farmStay")

plot_grid(fs_s20,fs_s70,nrow=1,rel_widths = c(1,1.3))

```


## Recruitment: *Habfactor*

```{r just_habFact}

hf20<-sfh%>%
  filter(size==0.2)%>%
  filter(farmStay==1)

hf_s20<-ggplot(hf20,aes(year,ppue,color=as.factor(habFact),group=as.factor(habFact)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 20%")+
  theme(legend.position = "none")


hf70<-sfh%>%
  filter(size==0.7)%>%
  filter(farmStay==1)

hf_s70<-ggplot(hf70,aes(year,ppue,color=as.factor(habFact),group=as.factor(habFact)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 70%")+
  scale_color_discrete(name="habFactor")

plot_grid(hf_s20,hf_s70,nrow=1,rel_widths = c(1,1.3))

```

***

## All

```{r all_farmStay}

afs20<-sfh%>%
  filter(size==0.2)%>%
  filter(habFact==4)

afs_s20<-ggplot(afs20,aes(year,ppue,color=as.factor(farmStay),group=as.factor(farmStay)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 20%")+
  theme(legend.position = "none")


afs70<-sfh%>%
  filter(size==0.7)%>%
  filter(habFact==4)

afs_s70<-ggplot(afs70,aes(year,ppue,color=as.factor(farmStay),group=as.factor(farmStay)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 70%")+
  scale_color_discrete(name="farmStay")

plot_grid(afs_s20,afs_s70,nrow=1,rel_widths = c(1,1.3))
```

```{r all_habFact}

ahf20<-sfh%>%
  filter(size==0.2)%>%
  filter(farmStay==10)

ahf_s20<-ggplot(ahf20,aes(year,ppue,color=as.factor(habFact),group=as.factor(habFact)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 20%")+
  theme(legend.position = "none")


ahf70<-sfh%>%
  filter(size==0.7)%>%
  filter(farmStay==10)

ahf_s70<-ggplot(ahf70,aes(year,ppue,color=as.factor(habFact),group=as.factor(habFact)))+
  geom_line()+
  theme_bw()+
  lims(y=c(9,16))+
  labs(y="Price / effort",title = "Farm size = 70%")+
  scale_color_discrete(name="habFactor")

plot_grid(ahf_s20,ahf_s70,nrow=1,rel_widths = c(1,1.3))

```